Measurement of total hadronic differential cross sections in the LArIAT experiment

### 2018-04-08 Chapter-1/1-Theory.tex
s

For this analysis, kaons are selected from the LArIAT beamline in the momentum range between \textcolor{red}{500} MeV/c and \textcolor{red}{1000} MeV/c (see Fig \ref{fig:TOFK}).

\begin{figure}[hpbt]
\centering
%\includegraphics[width=5in]{Chapter-1/Images/KaonTOF}
\caption{Time of flight versus momentum distributions as produced by the LArIAT TOF and Wire Chambers systems. The Kaon population lies between the proton and the muon/pion populations, allowing PID of Kaons in the beam line.  }
\label{fig:TOFK}
\end{figure}

In this energy range, the relevant K-Nucleon interactions are according to \cite{fesbach1992theoretical}:
\begin{equation}
K^{+} + N \rightarrow K^{+} + N\textit{ (elastic)}
\end{equation}
\begin{equation}K^{+} + n \rightarrow K^{0} + p\textit{ (elastic)}\end{equation}
\begin{equation}K^{+} + N \rightarrow K + N + \pi \textit{ (inelastic)}\end{equation}
\begin{equation}K^{+} + N \rightarrow K^{*} + N\textit{ (inelastic)}.\end{equation}

>>>>

%For this analysis, kaons are selected from the LArIAT beamline in the momentum range between \textcolor{red}{500} MeV/c and \textcolor{red}{1000} MeV/c (see Fig \ref{fig:TOFK}).

%\begin{figure}[hpbt]
%\centering
%\includegraphics[width=5in]{Chapter-1/Images/KaonTOF}
%\caption{Time of flight versus momentum distributions as produced by the LArIAT TOF and Wire Chambers systems. The Kaon population lies between the proton and the muon/pion populations, allowing PID of Kaons in the beam line.  }
%\label{fig:TOFK}
%\end{figure}

For the LArIAT cross section analysis, the kaons considered span a momentum inside the TPC from 800 MeV/c and 100 MeV/c. In this energy range, the relevant K-Nucleon interactions are according to \cite{fesbach1992theoretical}:

\begin{align}
K^{+} + N &\rightarrow K^{+} + N\textit{ (elastic)}\\
K^{+} + n &\rightarrow K^{0} + p\textit{ (elastic)}\\
K^{+} + N &\rightarrow K + N + \pi \textit{ (inelastic)}\\
K^{+} + N &\rightarrow K^{*} + N\textit{ (inelastic)}.
\end{align}

### 2018-04-08 Chapter-2/2-LArTPCs.tex
s

@@

>>>>

\begin{figure}[hbpt]
\centering
\includegraphics[width=3.5in]{Chapter-2/Images/pdkGenie.png}
\caption{Momentum of the kaon outgoing a proton decay event as simulated by the Genie 2.8.10 event generator in argon. The red line represent the kaon momentum distribution before undergoing the simulated final state interaction inside the argon nucleus, while the blue line represents the momentum distribution after FSI. }
\label{fig:PDKGENIE}
\end{figure}

@@

\textcolor{red}{ADD genie proton decay kaon distribution and lariat beamline overlaied}
The signature of a proton decay event in the ``LAr golden mode" is the presence of a single kaon of about 400 MeV in the detector.
